\textbf{Differences in COVID-19 vaccination in the province of Ontario across Health Regions and socio-economic strata}

### 2023-04-17 manuscript_v3/04-discussion.qmd
Fixed model, discussion, appendix

There existence of healthcare disparities within Ontario is a topic of particular interest as it motivated the recent change in the healthcare system of this region, which a system based on Health Regions in late 2019 in an attempt to address the disparities from the LHIN model  [@tsasis2012;@dong2022]. In this context, analyzing COVID-19 vaccination estimates within the province is important as they can provide an initial assessment of variations that might need to be addressed by decision-makers.

Our results indicate that across the most densely populated Health Regions of Ontario, almost three quarters of the surveyed individuals reported having received the first dose of the COVID-19 vaccine (@tbl-descriptive-stats). It is worth mentioning that province-wide vaccination rates for the period of interest are somewhat different from those of the survey, particularly in the case of those 55 years of age and older, which in the survey had a vaccination rate of 72\%, against a rate of 88.4\% reported for the closest age bracket (50 years of age and older) reported by Public Health Ontario at the start of the period covered by the data (between October 1st, 2021 and December 12th, 2021) [@ontario-covid]. In this regard, differences are to be expected because the survey represents a random sample from the population, and therefore, the sampling process is likely to cause variations between the values from the survey and province-wide estimates.

We believe that these differences did not have a significant impact in our analyses, because our results indicate that there were no significant differences in vaccination odds among the age groups considered in the survey, in agreement with the overall vaccination rates reported for Canada, which have been relatively higher when compared to other high income countries [@dube2022], and with vaccination uptake rates across different age groups presented in other studies [@macdonald2021;@guay2022]. Moreover, vaccination rates within each age in the dataset are in good agreement with province-wide estimates (e.g., a rate of 95\% for those with 61 years of age, Supplementary Table A-6). Additionally, when overall vaccination rates for the province are disaggregated, it can be seen that regional differences were present during the period analyzed, which can be masked by province-wide estimates. For example, the Public Health Unit of Lambton (a region within the West Health Region) and the Public Health Unit of Haliburton, Kawartha, and the Pine Ridge District (an area covered by the East Health Region) reported lower vaccination rates (78\%) for those 50 years of age and older at the beginning of the period of interest, whereas other regions had higher vaccination rates [@ontario-covid]. To this day, differences in vaccination rates within the province are present, because according to Public Health Ontario, as of March of 2023 some regions have less than 75\% vaccination rate [@ontario-covid-map]. Overall, these reasons indicate that the estimates obtained from the data are in good agreement with the trends from the population.

@@

According to Ontario Health, 13.2% of the population in the West Health Region identifies as a visible minority, whereas 2.5% identifies as Indigenous [@ontariohealth]. In the case of this analysis, the estimated lower odds are likely to be explained from a socio-economic perspective. In fact, 50% of the answers from this region in the survey came from the former LHINs of Hamilton Niagara Haldimand Brant, and Erie St. Clair, both which are among the regions of Ontario with the highest proportion of their population (more than 20%) in the lowest income quintile [@buajitti2018] (Supplementary Table A-8). Therefore, this result partly reinforces the well-known existing association between low vaccination rates and income, but it additionally indicates that there were intra-regional differences in vaccination. Interestingly, a disproportionate number of COVID-19 cases and low vaccination rate (under 50%) have been previously reported in the South Asian community of Ontario [@anand2022]; in this regard, our result provides additional context  by showing that within the South Asian community, there were differences in vaccination uptake across Ontario. Moreover, because significant lower odds of vaccination were also identified  other minority groups, this provides a rationale for future studies that explore how vaccination uptake varies across different minority groups within Ontario and other Canadian provinces.

>>>>

The existence of healthcare disparities in Ontario motivated the recent change in the healthcare system of the province, which changed the LHIN model for a Health Region model in late 2019  [@tsasis2012;@dong2022]. In this context, analyzing COVID-19 vaccination estimates between the Health Regions can serve as an indicator of ongoing intra-provincial disparities that may need to be addressed to ensure that the Health Region model is able to improve health access for the inhabitants of Ontario, which faces unique challenges due to its condition as the most populated and the most ethnically diverse province of Canada.

Our results indicate that across the most densely populated Health Regions of Ontario, almost three quarters of surveyed individuals reported to have received the first dose of the COVID-19 vaccine (@tbl-descriptive-stats). It is worth mentioning that province-wide vaccination rates for the period of interest are somewhat different from those of the survey, particularly in the case of those 55 years of age and older, which in the survey had a vaccination rate of 72\%, against a rate of 88.4\% reported for the closest age bracket (50 years of age and older) reported by Public Health Ontario at the start of the period covered by the data (between October 1st, 2021 and December 12th, 2021) [@ontario-covid]. In this case, differences between the survey and province-wide estimates are to be expected as the data from survey represents a random sample from the overall population.

However, this variation did not lead to discrepant results, as the estimates from the model indicate that no significant differences in vaccination odds were identified among the age groups analyzed, in agreement with both overall vaccination rates reported for Canada, which have been relatively higher when compared to other high income countries [@dube2022], and with vaccination uptake rates across different age groups presented in other studies [@macdonald2021;@guay2022]. In other words, although vaccination rates obtained from the survey were slightly lower than the provincial estimates, these values still represented a valid approximation; this notion is reinforced by the consistency in the proportion of vaccination rates (@tbl-descriptive-stats) and vaccination odds (@tbl-model) across the period covered by the survey, which follow the vaccination rates from Public Health Ontario and which indicate that due to the relatively high coverage achieved in the population at that point, there were no abrupt shift in the trends, which increased by around 3% across all age groups during the three months (October, November, and December of 2021 [@ontario-covid]). Moreover, there was good agreement between vaccination rates within each age in the raw dataset and province-wide estimates (e.g., a rate of 95\% for those with 61 years of age, Supplementary Table A-6, which is similar to the value reported by Public Health Ontario). It is also important to mention that regional differences can be masked by overall estimates, as when overall vaccination rates for the province (from Public Health Ontario) are disaggregated, it can be seen that regional differences during the period analyzed existed. For example, the Public Health Unit of Lambton (a region within the West Health Region) and the Public Health Unit of Haliburton, Kawartha, and the Pine Ridge District (an area covered by the East Health Region) reported lower vaccination rates (78\%) for those 50 years of age and older at the beginning of the period of interest, in contrast with other regions that had vaccination rates above 80\% [@ontario-covid]. To this day, differences in vaccination rates within the province continue, as according to Public Health Ontario, as of March of 2023 some regions still have less than 75\% vaccination rate [@ontario-covid-map].

@@

According to Ontario Health, 13.2% of the population in the West Health Region identifies as a visible minority, whereas 2.5% identifies as Indigenous [@ontariohealth]. In the case of this analysis, the estimated lower odds are likely to be explained from a socio-economic perspective. In fact, 50% of the answers from this region in the survey came from the former LHINs of Hamilton Niagara Haldimand Brant, and Erie St. Clair, both which are among the regions of Ontario with the highest proportion of their population (more than 20%) in the lowest income quintile [@buajitti2018] (Supplementary Table A-8). Therefore, this result partly reinforces the well-known existing association between low vaccination rates and income, but it additionally indicates that there were intra-regional differences in vaccination. Interestingly, a disproportionate number of COVID-19 cases and low vaccination rate (under 50%) have been previously reported in the South Asian community of Ontario [@anand2022]; in this regard, our result provides additional context  by showing that within the South Asian community, there were differences in vaccination uptake across Ontario. Moreover, because significant lower odds of vaccination were also identified in other minority groups, this provides a rationale for future studies that explore how vaccination uptake varies across different minority groups within Ontario and other Canadian provinces.

### 2023-04-17 manuscript_v3/appendix.qmd
Fixed model, discussion, appendix

---
title: '**COVID-19 vaccination in Ontario: Exploring intra-provincial variations within Health Regions and socio-economic strata**'
subtitle: Appendix
authors:
  - name: Ariel Mundo Ortiz
    affiliations:
      - ref: crm
    email: ariel.mundo.ortiz@umontreal.ca
    orcid: 0000-0002-6014-4538
  - name: Bouchra Nasri
    affiliations:
      - ref: espum
    email: bouchra.nasri@umontreal.ca
    corresponding: true
affiliations:
  - id: crm
    name: Centre de Recherches Mathématiques, University of Montreal, Montréal, Canada
  - id: espum
    name: Department of Social and Preventive Medicine, École de Santé Publique, University of Montreal, Montréal, Canada 
filters:
  - authors-block
format: 
  pdf:
    #mainfont: "Palatino Linotype"
    include-before-body: latex/appendix_preamble.sty
linestretch: 2
keep-tex: true
---

```{r, setup, echo=FALSE}
#| warning: false
library(tidyverse)
library(magrittr)
library(here)
library(patchwork)
library(gt)
library(gtsummary)
library(survey)
library(emmeans)
library(scico)

@@

  ggplot(p2%>%count(Age_group_ord) %>%    # G count number in each group
         mutate(pct=n/sum(n),               # Calculate percent within each group
                ypos = 200),  # Calculate label positions
       aes(Age_group_ord, n, fill=Age_group_ord)) +
  geom_bar(stat="identity") +
  geom_text(aes(label=paste0(sprintf("%1.1f", pct*100),"%"), y=ypos))+
  theme_classic()+
  thm1

@@

```{r,interaction-race-income}
#| echo: false
#| warning: false
#| fig-height: 4
#| fig-width: 6
#| fig-cap: Estimated marginal means for the combination between Race and Income in the regression model.

race_income<-emmip(m1, Race ~ income_ord, CIs=TRUE,plotit = FALSE)

@@

```{r,interaction-race-hr}
#| echo: false
#| warning: false
#| fig-height: 4
#| fig-width: 6
#| fig-cap: Estimated marginal means for the combination between Race and Health Region in the regression model.

race_hr<-emmip(m1, Race ~ Health_Region, CIs=TRUE,plotit = FALSE)

@@

clean_data %>% subset (Race=="white_caucasian")%>%
  tbl_summary(
    percent="row",
    by= first_dose,
    include=c(Health_Region),
    sort = all_categorical() ~ "frequency"
  ) %>% bold_labels()%>%
  as_kable_extra(booktabs = TRUE,linesep="")
```

@@

# clean_data %>% subset (LHIN=="Hamilton Niagara Haldimand Brant (Hnhb)")%>%
# tbl_summary(include=c(Race),
#             sort = all_categorical() ~ "frequency") %>% 
#   bold_labels()
# 
# 
# clean_data %>% subset (LHIN=="Hamilton Niagara Haldimand Brant (Hnhb)")%>%
# tbl_summary(by=first_dose,
#             percent="row",
#   include=c(Race),
#             sort = all_categorical() ~ "frequency") %>% 
#   bold_labels()
# 
# clean_data %>% subset (LHIN=="Erie St. Clair")%>%
# tbl_summary(by=first_dose,
#             percent="row",
#   include=c(Race),
#             sort = all_categorical() ~ "frequency") %>% 
#   bold_labels()
```

>>>>

---
title: '**Differences in COVID-19 vaccination in the province of Ontario across Health Regions and socio-economic strata**'
subtitle: Appendix
authors:
  - name: Ariel Mundo Ortiz
    affiliations:
      - ref: crm
      - ref: espum
    email: ariel.mundo.ortiz@umontreal.ca
    orcid: 0000-0002-6014-4538
  - name: Bouchra Nasri
    affiliations:
      - ref: crm
      - ref: espum
    email: bouchra.nasri@umontreal.ca
    corresponding: true
affiliations:
  - id: crm
    name: Centre de Recherches Mathématiques, University of Montreal, Montréal, Canada
  - id: espum
    name: Department of Social and Preventive Medicine, École de Santé Publique, University of Montreal, Montréal, Canada 
filters:
  - authors-block
format: 
  pdf:
    #mainfont: "Palatino Linotype"
    include-before-body: latex/appendix_preamble.sty
linestretch: 2
keep-tex: true
---

```{r, setup, echo=FALSE}
#| warning: false
library(tidyverse)
library(magrittr)
library(here)
library(patchwork)
library(gt)
library(lubridate)
library(gtsummary)
library(survey)
library(emmeans)
library(scico)

@@

  ggplot(p2%>%count(Age_group_ord) %>%    # G count number in each group
         mutate(pct=n/sum(n),               # Calculate percent within each group
                ypos = 200),  # Calculate label positions
       aes(Age_group_ord, n, fill=Age_group_ord)) +
  geom_bar(stat="identity") +
    xlab("Age group")+
  geom_text(aes(label=paste0(sprintf("%1.1f", pct*100),"%"), y=ypos))+
  theme_classic()+
  thm1

@@

```{r,interaction-race-income}
#| echo: false
#| warning: false
#| fig-height: 4
#| fig-width: 6
#| fig-cap: Estimated marginal means for the interaction between Race and Income in the regression model.

race_income<-emmip(m2, Race ~ income_ord, CIs=TRUE,plotit = FALSE)

@@

```{r,interaction-race-hr}
#| echo: false
#| warning: false
#| fig-height: 4
#| fig-width: 6
#| fig-cap: Estimated marginal means for the interaction between Race and Health Region in the regression model.

race_hr<-emmip(m2, Race ~ Health_Region, CIs=TRUE,plotit = FALSE)

@@

clean_data %>% subset (Race=="White/Caucasian")%>%
  tbl_summary(
    percent="row",
    by= first_dose,
    include=c(Health_Region),
    sort = all_categorical() ~ "frequency"
  ) %>% bold_labels()%>%
  as_kable_extra(booktabs = TRUE,linesep="")
```

@@

### 2023-04-17 manuscript_v3/appendix.tex
Fixed model, discussion, appendix

\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\KOMAoption{captions}{tableheading}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={COVID-19 vaccination in Ontario: Exploring intra-provincial variations within Health Regions and socio-economic strata},
  pdfauthor={Ariel Mundo Ortiz1; Bouchra Nasri2,},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{\textbf{COVID-19 vaccination in Ontario: Exploring
intra-provincial variations within Health Regions and socio-economic
strata}}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Appendix}
\author{Ariel Mundo Ortiz\textsuperscript{1} \and Bouchra
Nasri\textsuperscript{2,*}}
\date{}

@@

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, interior hidden, frame hidden, breakable, sharp corners, boxrule=0pt, enhanced]}{\end{tcolorbox}}\fi

@@

\toprule
Race & observations & percentage \\ 
\midrule
white\_caucasian & 1313 & $37.0\%$ \\ 
arab\_middle\_eastern & 214 & $6.0\%$ \\ 
black & 298 & $8.4\%$ \\ 
east\_asian\_pacific\_islander & 303 & $8.5\%$ \\ 
indigenous & 191 & $5.4\%$ \\ 
latin\_american & 180 & $5.1\%$ \\ 
mixed & 310 & $8.7\%$ \\ 
other & 367 & $10.3\%$ \\ 
south\_asian & 375 & $10.6\%$ \\ 
\bottomrule
\end{longtable}

@@

\toprule
\textbf{Characteristic} & \textbf{no}, N = 958 & \textbf{yes}, N = 2,593\\
\midrule
\endfirsthead
\multicolumn{3}{@{}l}{\textit{(continued)}}\\
\toprule
\textbf{Characteristic} & \textbf{no}, N = 958 & \textbf{yes}, N = 2,593\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
\textbf{Age} &  & \\
\hspace{1em}16 & 11 (21\%) & 41 (79\%)\\
\hspace{1em}17 & 15 (25\%) & 45 (75\%)\\
\hspace{1em}18 & 53 (36\%) & 93 (64\%)\\
\hspace{1em}19 & 33 (31\%) & 74 (69\%)\\
\hspace{1em}20 & 18 (17\%) & 85 (83\%)\\
\hspace{1em}21 & 30 (25\%) & 92 (75\%)\\
\hspace{1em}22 & 19 (23\%) & 62 (77\%)\\
\hspace{1em}23 & 21 (24\%) & 67 (76\%)\\
\hspace{1em}24 & 23 (29\%) & 55 (71\%)\\
\hspace{1em}25 & 25 (24\%) & 80 (76\%)\\
\hspace{1em}26 & 23 (30\%) & 53 (70\%)\\
\hspace{1em}27 & 16 (25\%) & 49 (75\%)\\
\hspace{1em}28 & 13 (20\%) & 52 (80\%)\\
\hspace{1em}29 & 13 (26\%) & 37 (74\%)\\
\hspace{1em}30 & 12 (21\%) & 44 (79\%)\\
\hspace{1em}31 & 17 (38\%) & 28 (62\%)\\
\hspace{1em}32 & 17 (27\%) & 47 (73\%)\\
\hspace{1em}33 & 17 (26\%) & 48 (74\%)\\
\hspace{1em}34 & 33 (35\%) & 60 (65\%)\\
\hspace{1em}35 & 31 (34\%) & 59 (66\%)\\
\hspace{1em}36 & 16 (25\%) & 49 (75\%)\\
\hspace{1em}37 & 15 (30\%) & 35 (70\%)\\
\hspace{1em}38 & 10 (28\%) & 26 (72\%)\\
\hspace{1em}39 & 5 (16\%) & 26 (84\%)\\
\hspace{1em}40 & 7 (16\%) & 36 (84\%)\\
\hspace{1em}41 & 5 (14\%) & 31 (86\%)\\
\hspace{1em}42 & 7 (19\%) & 30 (81\%)\\
\hspace{1em}43 & 9 (17\%) & 45 (83\%)\\
\hspace{1em}44 & 24 (33\%) & 48 (67\%)\\
\hspace{1em}45 & 23 (30\%) & 53 (70\%)\\
\hspace{1em}46 & 13 (24\%) & 41 (76\%)\\
\hspace{1em}47 & 18 (37\%) & 31 (63\%)\\
\hspace{1em}48 & 10 (33\%) & 20 (67\%)\\
\hspace{1em}49 & 8 (28\%) & 21 (72\%)\\
\hspace{1em}50 & 7 (16\%) & 38 (84\%)\\
\hspace{1em}51 & 7 (23\%) & 23 (77\%)\\
\hspace{1em}52 & 9 (20\%) & 36 (80\%)\\
\hspace{1em}53 & 9 (22\%) & 31 (78\%)\\
\hspace{1em}54 & 19 (37\%) & 33 (63\%)\\
\hspace{1em}55 & 12 (23\%) & 41 (77\%)\\
\hspace{1em}56 & 13 (26\%) & 37 (74\%)\\
\hspace{1em}57 & 12 (22\%) & 43 (78\%)\\
\hspace{1em}58 & 6 (14\%) & 38 (86\%)\\
\hspace{1em}59 & 4 (12\%) & 28 (88\%)\\
\hspace{1em}60 & 3 (11\%) & 25 (89\%)\\
\hspace{1em}61 & 1 (4.5\%) & 21 (95\%)\\
\hspace{1em}62 & 8 (26\%) & 23 (74\%)\\
\hspace{1em}63 & 5 (19\%) & 21 (81\%)\\
\hspace{1em}64 & 11 (33\%) & 22 (67\%)\\
\hspace{1em}65 & 11 (20\%) & 45 (80\%)\\
\hspace{1em}66 & 11 (28\%) & 28 (72\%)\\
\hspace{1em}67 & 8 (22\%) & 28 (78\%)\\
\hspace{1em}68 & 5 (19\%) & 21 (81\%)\\
\hspace{1em}69 & 17 (39\%) & 27 (61\%)\\
\hspace{1em}70 & 4 (14\%) & 24 (86\%)\\
\hspace{1em}71 & 1 (3.8\%) & 25 (96\%)\\
\hspace{1em}72 & 2 (9.1\%) & 20 (91\%)\\
\hspace{1em}73 & 3 (12\%) & 22 (88\%)\\
\hspace{1em}74 & 13 (31\%) & 29 (69\%)\\
\hspace{1em}98 & 147 (42\%) & 201 (58\%)\\*
\multicolumn{3}{l}{\rule{0pt}{1em}\textsuperscript{1} n (\%)}\\
\end{longtable}

@@

\caption{Estimated marginal means for the combination between Race and
Income in the regression model.}

@@

\caption{Estimated marginal means for the combination between Race and
Health Region in the regression model.}

@@

\centering
\begin{tabular}{lcc}
\toprule
\textbf{Characteristic} & \textbf{no}, N = 233 & \textbf{yes}, N = 1,080\\
\midrule
\textbf{Health\_Region} &  & \\
\hspace{1em}Toronto & 85 (21\%) & 321 (79\%)\\
\hspace{1em}West & 69 (17\%) & 329 (83\%)\\
\hspace{1em}East & 41 (15\%) & 236 (85\%)\\
\hspace{1em}Central & 38 (16\%) & 194 (84\%)\\
\bottomrule
\multicolumn{3}{l}{\rule{0pt}{1em}\textsuperscript{1} n (\%)}\\
\end{tabular}
\end{table}

>>>>

\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\KOMAoption{captions}{tableheading}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Differences in COVID-19 vaccination in the province of Ontario across Health Regions and socio-economic strata},
  pdfauthor={Ariel Mundo Ortiz1,2; Bouchra Nasri1,2,},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{\textbf{Differences in COVID-19 vaccination in the province of
Ontario across Health Regions and socio-economic strata}}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Appendix}
\author{Ariel Mundo Ortiz\textsuperscript{1,2} \and Bouchra
Nasri\textsuperscript{1,2,*}}
\date{}

@@

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, interior hidden, enhanced, breakable, frame hidden, sharp corners]}{\end{tcolorbox}}\fi

@@

\toprule
Race & observations & percentage \\ 
\midrule
White/Caucasian & 1312 & $37.0\%$ \\ 
Arab/Middle Eastern & 214 & $6.0\%$ \\ 
Black & 298 & $8.4\%$ \\ 
East Asian/Pacific Islander & 303 & $8.5\%$ \\ 
Indigenous & 191 & $5.4\%$ \\ 
Latin American & 180 & $5.1\%$ \\ 
Mixed & 310 & $8.7\%$ \\ 
Other & 367 & $10.3\%$ \\ 
South Asian & 374 & $10.5\%$ \\ 
\bottomrule
\end{longtable}

@@

\toprule
\textbf{Characteristic} & \textbf{no}, N = 958 & \textbf{yes}, N = 2,591\\
\midrule
\endfirsthead
\multicolumn{3}{@{}l}{\textit{(continued)}}\\
\toprule
\textbf{Characteristic} & \textbf{no}, N = 958 & \textbf{yes}, N = 2,591\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
\textbf{Age} &  & \\
\hspace{1em}16 & 11 (21\%) & 41 (79\%)\\
\hspace{1em}17 & 15 (25\%) & 45 (75\%)\\
\hspace{1em}18 & 53 (36\%) & 93 (64\%)\\
\hspace{1em}19 & 33 (31\%) & 74 (69\%)\\
\hspace{1em}20 & 18 (17\%) & 85 (83\%)\\
\hspace{1em}21 & 30 (25\%) & 92 (75\%)\\
\hspace{1em}22 & 19 (23\%) & 62 (77\%)\\
\hspace{1em}23 & 21 (24\%) & 67 (76\%)\\
\hspace{1em}24 & 23 (29\%) & 55 (71\%)\\
\hspace{1em}25 & 25 (24\%) & 80 (76\%)\\
\hspace{1em}26 & 23 (31\%) & 52 (69\%)\\
\hspace{1em}27 & 16 (25\%) & 49 (75\%)\\
\hspace{1em}28 & 13 (20\%) & 52 (80\%)\\
\hspace{1em}29 & 13 (26\%) & 37 (74\%)\\
\hspace{1em}30 & 12 (21\%) & 44 (79\%)\\
\hspace{1em}31 & 17 (38\%) & 28 (62\%)\\
\hspace{1em}32 & 17 (27\%) & 47 (73\%)\\
\hspace{1em}33 & 17 (26\%) & 48 (74\%)\\
\hspace{1em}34 & 33 (35\%) & 60 (65\%)\\
\hspace{1em}35 & 31 (34\%) & 59 (66\%)\\
\hspace{1em}36 & 16 (25\%) & 49 (75\%)\\
\hspace{1em}37 & 15 (30\%) & 35 (70\%)\\
\hspace{1em}38 & 10 (28\%) & 26 (72\%)\\
\hspace{1em}39 & 5 (16\%) & 26 (84\%)\\
\hspace{1em}40 & 7 (16\%) & 36 (84\%)\\
\hspace{1em}41 & 5 (14\%) & 31 (86\%)\\
\hspace{1em}42 & 7 (19\%) & 30 (81\%)\\
\hspace{1em}43 & 9 (17\%) & 45 (83\%)\\
\hspace{1em}44 & 24 (33\%) & 48 (67\%)\\
\hspace{1em}45 & 23 (30\%) & 53 (70\%)\\
\hspace{1em}46 & 13 (24\%) & 41 (76\%)\\
\hspace{1em}47 & 18 (37\%) & 31 (63\%)\\
\hspace{1em}48 & 10 (33\%) & 20 (67\%)\\
\hspace{1em}49 & 8 (28\%) & 21 (72\%)\\
\hspace{1em}50 & 7 (16\%) & 38 (84\%)\\
\hspace{1em}51 & 7 (23\%) & 23 (77\%)\\
\hspace{1em}52 & 9 (20\%) & 36 (80\%)\\
\hspace{1em}53 & 9 (22\%) & 31 (78\%)\\
\hspace{1em}54 & 19 (37\%) & 33 (63\%)\\
\hspace{1em}55 & 12 (23\%) & 41 (77\%)\\
\hspace{1em}56 & 13 (26\%) & 37 (74\%)\\
\hspace{1em}57 & 12 (22\%) & 43 (78\%)\\
\hspace{1em}58 & 6 (14\%) & 37 (86\%)\\
\hspace{1em}59 & 4 (12\%) & 28 (88\%)\\
\hspace{1em}60 & 3 (11\%) & 25 (89\%)\\
\hspace{1em}61 & 1 (4.5\%) & 21 (95\%)\\
\hspace{1em}62 & 8 (26\%) & 23 (74\%)\\
\hspace{1em}63 & 5 (19\%) & 21 (81\%)\\
\hspace{1em}64 & 11 (33\%) & 22 (67\%)\\
\hspace{1em}65 & 11 (20\%) & 45 (80\%)\\
\hspace{1em}66 & 11 (28\%) & 28 (72\%)\\
\hspace{1em}67 & 8 (22\%) & 28 (78\%)\\
\hspace{1em}68 & 5 (19\%) & 21 (81\%)\\
\hspace{1em}69 & 17 (39\%) & 27 (61\%)\\
\hspace{1em}70 & 4 (14\%) & 24 (86\%)\\
\hspace{1em}71 & 1 (3.8\%) & 25 (96\%)\\
\hspace{1em}72 & 2 (9.1\%) & 20 (91\%)\\
\hspace{1em}73 & 3 (12\%) & 22 (88\%)\\
\hspace{1em}74 & 13 (31\%) & 29 (69\%)\\
\hspace{1em}98 & 147 (42\%) & 201 (58\%)\\*
\multicolumn{3}{l}{\rule{0pt}{1em}\textsuperscript{1} n (\%)}\\
\end{longtable}

@@

\caption{Estimated marginal means for the interaction between Race and
Income in the regression model.}

@@

\caption{Estimated marginal means for the interaction between Race and
Health Region in the regression model.}

@@

\centering
\begin{tabular}{lcc}
\toprule
\textbf{Characteristic} & \textbf{no}, N = 233 & \textbf{yes}, N = 1,079\\
\midrule
\textbf{Health\_Region} &  & \\
\hspace{1em}Toronto & 85 (21\%) & 321 (79\%)\\
\hspace{1em}West & 69 (17\%) & 329 (83\%)\\
\hspace{1em}East & 41 (15\%) & 236 (85\%)\\
\hspace{1em}Central & 38 (16\%) & 193 (84\%)\\
\bottomrule
\multicolumn{3}{l}{\rule{0pt}{1em}\textsuperscript{1} n (\%)}\\
\end{tabular}
\end{table}
